---
title: "Groove Identification Using Hough Transforms"
author: "Charlotte Roiger"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


Hough transforms are a low-level computer vision algorithm used to detect basic shapes in an image array. The earliest case was for detecting a line in an image, but since then, has expanded to include circles and other such shapes. For bullet processing, the borders of a groove engraved area are often deep linear divets in a bullet land, so Hough transforms are useful for distinguishing between land engraved areas(LEAs) and groove engraved area(GEAs). We will cover the process of using Hough transforms to find GEAs from bullet pre-processing to method comparison. 

# Step One: Bullet Pre-Processing

We will use demo data available in the `grooveFinder` package to demonstrate how to find grooves using Hough transforms. It's important to note, that unlike other methods available in `grooveFinder`, `get_grooves_hough` requires the entirety of the x3p for analysis rather than a single or averaged crosscut. See package `x3ptools` at https://heike.github.io/x3ptools/ for ways to convert different file formats into x3p standard files. 

```{r warning = F, message= F}

# Load in Libraries

library(ggplot2) # Utilize to visualize cross cuts and bullet lands
library(dplyr) # Used to transform and cleaning up data
library(x3ptools) # Contains a host of useful functions for dealing with x3ps
library(bulletxtrctr) 
library(grooveFinder) 
```

The data we will be working with is from the Hamby 44 dataset from the NIST Research Ballistics Toolmarks data base (NRBTD)[https://tsapps.nist.gov/NRBTD/Studies/Search] These are commands loading the bullet scans into `R` without downloading the actual files.


```{r}
# Load in data using weblinks
b1 <- read_bullet(urllist = hamby44demo[[1]])
b2 <- read_bullet(urllist = hamby44demo[[2]])
```

For ease of use we will combine the data into one dataframe.

```{r}
b1$bullet <- 1
b2$bullet <- 2
b1$land <- 1:6
b2$land <- 1:6
bullets <- rbind(b1, b2)
```

The measurement of each scan should be in microns, however checking the units as shown below indicates that it is recorded in meters.

```{r}
bullets$x3p[[1]]$header.info$incrementY
```



